My title

### 2024-11-26 paper/paper.qmd
modified:   paper/paper.qmd

library(tidyverse)
library(here)
library(arrow)
library(corrplot)
library(knitr)
library(kableExtra)
library(car)
library(modelsummary)
library(brms)

@@

The R2 value calculated on the test data ($R^2 = 0.59$) is very close to the R2 value of the model on the training data ($R^2 = 0.61$), as discussed in @sec-result-r2 This similarity indicates that the model generalizes well to unseen data, as its performance on the test set is consistent with its performance during training. The small difference between the two R2 values suggests that the model is not overfitting the training data and captures the underlying relationships in the data effectively.

```{r}
#| label: tbl-test-validate
#| tbl-cap: R2 value on test data is close to train data
#| echo: false
#| warning: false

test_data$predicted <- predict(glm, newdata = test_data)
SSR <- sum((test_data$log_mean_temp - test_data$predicted)^2)  # Sum of Squared Residuals
TSS <- sum((test_data$log_mean_temp - mean(test_data$log_mean_temp))^2)  # Total Sum of Squares
R2 <- 1 - (SSR / TSS)
R2T <- summary(glm)$r.squared
results <- data.frame(
  Metric = c("SSR", "TSS", "R2", "R2-Train"),
  Value = c(SSR, TSS, R2, R2T)
)

@@

>>>>

library(tidyverse)
library(here)
library(arrow)
library(corrplot)
library(knitr)
library(kableExtra)
library(car)
library(modelsummary)
library(brms)
library(Metrics)

@@

The R2 value calculated on the test data ($R^2 = 0.59$) is very close to the R2 value of the model on the training data ($R^2 = 0.61$), as discussed in @sec-result-r2 This similarity indicates that the model generalizes well to unseen data, as its performance on the test set is consistent with its performance during training. The training MSE of 0.0137 and test MSE of 0.0158 indicate the model performs well on both datasets with minimal overfitting. The The small difference between the two R2 values and the small difference between the errors suggests good generalization to unseen data.

```{r}
#| label: tbl-test-validate
#| tbl-cap: R2 and MSE value on test data is close to train data
#| echo: false
#| warning: false

test_data$predicted <- predict(glm, newdata = test_data)
SSR <- sum((test_data$log_mean_temp - test_data$predicted)^2)  # Sum of Squared Residuals
TSS <- sum((test_data$log_mean_temp - mean(test_data$log_mean_temp))^2)  # Total Sum of Squares
R2 <- 1 - (SSR / TSS)
R2T <- summary(glm)$r.squared

train_predictions <- predict(glm, newdata = train_data)
test_predictions <- predict(glm, newdata = test_data)

y_train <- train_data$log_mean_temp
y_test <- test_data$log_mean_temp

mse_train <- mse(y_train, train_predictions)
mse_test <- mse(y_test, test_predictions)

results <- data.frame(
  Metric = c("SSR", "TSS", "R2", "R2-Train", "MSE-Train", "MSE-Test"),
  Value = c(SSR, TSS, R2, R2T, mse_train, mse_test)
)

@@

```{r}
